---
title: "Flight data"
author: "christianbomholt"
date: "September 24, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```


# Airline Service Quality Performance 234 (On-Time performance data)

This data has been reported by U.S. certificated air carriers so that information on the air carriers' quality of service can be made available to consumers of air transportation.

Carriers within 1% or more of the total domestic scheduled service passenger revenues are required to report data for flights involving any airport in the 48 contiguous states accounting for 1% or more of the domestic scheduled service passenger enplanements. The regulation also provides for the voluntary reporting of a carrier's entire domestic system and voluntary reporting by other carriers. Some of the data elements included are departure, arrival, and elapsed flight times as shown by the Official Airline Guide; the carrier's computer reservation system and the carrier's actual performance; and selected differences among the three sources, such as delay and elapsed time difference.

## Import data

```{r}
library(ggplot2)
library(dplyr)
library(DT)
```


```{r}
flightCSV <- "../data/flight_data/2000.csv"

flightDF <- read.csv(flightCSV,nrows = 1e5)[,-1]
datatable(head(flightDF, 10), options = list('t'))
```

```{r}
print(head(flightDF))
```


```{r}
flightDF <- flightDF %>%
  mutate(Date = as.Date(
    paste0(
      Year,"-",Month,"-",DayofMonth
    )
  )) 
```


## Vizualize general dynamics

```{r}
library(ggplot2)
library(dplyr)
ggplot(data = flightDF) +
  geom_point(mapping = aes(x = Date, y = ArrDelay), alpha = 5/50) +
  xlab("Date") +
  ylab("Arrival Delay in minutes")
```


```{r}
library(stringr)
xtabs(~Origin+Month,flightDF %>% 
filter(str_detect(Origin, "^ABE|^ABQ")) %>% droplevels())
```

## More advanced cross-tabbing



## Linear models

```{r}
model <- lm(ArrDelay ~ as.numeric(Date),flightDF)
summary(model)
```
```{r}
library(broom)
tidy(summary(model))
```

```{r}
ggplot(flightDF,aes(Date,ArrDelay))+
  geom_point(alpha = 5/50)+
  geom_smooth(method='lm')
```


## Measuring runtime

```{r}
system.time(gaussianMean<-mean(rnorm(10000)))
```

```{r,eval=FALSE}
 ?proc.time
```


>The first two entries are the total user and system CPU times of the current 
R process and any child processes on which it has waited, and the
third entry is the ‘real’ elapsed time since the process was started.

>The definition of ‘user’ and ‘system’ times is from your OS.
Typically it is something like _The ‘user time’ is the CPU time charged for the execution of user
instructions of the calling process. The ‘system time’ is the CPU
time charged for execution by the system on behalf of the calling process._

## Read from SQL

```{r}
library(DBI)
library(RSQLite)
con <- dbConnect(SQLite(), dbname="../data/flight_data/airports.sqlite")
dbReadTable(con, "airport") %>% head
```


